---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(magrittr)
```

# NOAA Integrated Surface Database (ISD)

Preview this [Data Package](http://specs.frictionlessdata.io/data-packages/) using the [Data Package Viewer](http://data.okfn.org/tools/view?url=https://github.com/columbia-glacier/noaa-isd).

## Data

### Description

The data includes meteorological observations from nearby weather stations ([map](https://gis.ncdc.noaa.gov/maps/ncei/cdo/hourly)):

  * Valdez (National) Weather Service Office
    * 702750-[26442](https://www.ncdc.noaa.gov/cdo-web/datasets/LCD/stations/WBAN:26442/detail)
    * 999999-[26442](https://www.ncdc.noaa.gov/cdo-web/datasets/LCD/stations/WBAN:26442/detail)
  * Valdez Pioneer Field Airport
    * 702756-[26479](https://www.ncdc.noaa.gov/cdo-web/datasets/LCD/stations/WBAN:26479/detail)
    * 702756-99999
    * 702754-99999
  * 998271-99999 Valdez
  * 994660-99999 Potato Point
  * 994670-99999 Middle Rock Light
  * 994680-99999 Bligh Reef Light
  * 997203-99999 Western Prince William Sound
  * 992850-99999 West Orca Bay
  
```{r, fig.height=10, fig.width=10}
dp <- dpkg::read_package()
stations <- dp$stations
dp$stations <- NULL
data <- data.table::rbindlist(dp, fill = TRUE, idcol = "station_id")
cols <- names(data) %>%
  extract(!grepl("_quality$|_uncertainty$|_period$", .))
ranges <- cgr::tblranges(
  data[, cols, with = FALSE],
  time_col = "t",
  group_col = "station_id",
  maxdt = 60 * 60 * 24
)
ranges$station <- ranges$station_id %>%
  match(stations$id) %>%
  extract(stations$name, .) %>%
  paste(ranges$station_id, .)
cgr::timeline(ranges, name = "station", group = "variable", color = "gray40", width = 3) +
  ggplot2::xlab("Year") +
  ggplot2::ggtitle("Observational coverage", subtitle = "sampled at daily intervals")
```

### Sources

[NOAA Integrated Surface Database FTP Access](ftp://ftp.ncdc.noaa.gov/pub/data/noaa/)
